### 2020-08-28 rR.tex
still making so many changes!!
update

% Created by tikzDevice version 0.12.3 on 2020-04-29 03:55:17
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 52.94,254.97) --
	( 55.54,255.77) --
	( 58.13,256.58) --
	( 60.73,257.40) --
	( 63.32,258.23) --
	( 65.92,259.08) --
	( 68.51,259.94) --
	( 71.11,260.81) --
	( 73.70,261.69) --
	( 76.30,262.59) --
	( 78.89,263.49) --
	( 81.49,264.42) --
	( 84.08,265.35) --
	( 86.68,266.30) --
	( 89.27,267.26) --
	( 91.87,268.23) --
	( 94.46,269.21) --
	( 97.06,270.20) --
	( 99.65,271.21) --
	(102.25,272.23) --
	(104.84,273.26) --
	(107.44,274.30) --
	(110.03,275.36) --
	(112.63,276.43) --
	(115.22,277.51) --
	(117.82,278.61) --
	(120.41,279.72) --
	(123.01,280.84) --
	(125.60,281.98) --
	(128.20,283.13) --
	(130.79,284.29) --
	(133.39,285.46) --
	(135.98,286.65) --
	(138.58,287.85) --
	(141.17,289.07) --
	(143.77,290.31) --
	(146.36,291.55) --
	(148.96,292.82) --
	(151.55,294.10) --
	(154.15,295.40) --
	(156.74,296.71) --
	(159.34,298.04) --
	(161.93,299.39) --
	(164.53,300.75) --
	(167.12,302.12) --
	(169.72,303.51) --
	(172.31,304.92) --
	(174.91,306.34) --
	(177.51,307.78) --
	(180.10,309.24) --
	(182.70,310.71) --
	(185.29,312.21) --
	(187.89,313.72) --
	(190.48,315.26) --
	(193.08,316.81) --
	(195.67,318.38) --
	(198.27,319.97) --
	(200.86,321.57) --
	(203.46,323.20) --
	(206.05,324.84) --
	(208.65,326.51) --
	(211.24,328.19) --
	(213.84,329.89) --
	(216.43,331.62) --
	(219.03,333.36) --
	(221.62,335.12) --
	(224.22,336.91) --
	(226.81,338.72) --
	(229.41,340.54) --
	(232.00,342.39) --
	(234.60,344.25) --
	(237.19,346.14) --
	(239.79,348.04) --
	(242.38,349.97) --
	(244.98,351.91) --
	(247.57,353.87) --
	(250.17,355.85) --
	(252.76,357.85) --
	(255.36,359.88) --
	(257.95,361.92);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.52) --
	( 30.34,248.34) --
	( 33.37,249.16) --
	( 36.40,250.01) --
	( 39.42,250.87) --
	( 42.45,251.74) --
	( 45.48,252.64) --
	( 48.51,253.54) --
	( 51.53,254.47) --
	( 54.56,255.41) --
	( 57.59,256.36) --
	( 60.62,257.34) --
	( 63.64,258.32) --
	( 66.67,259.33) --
	( 69.70,260.35) --
	( 72.73,261.38) --
	( 75.76,262.43) --
	( 78.78,263.50) --
	( 81.81,264.58) --
	( 84.84,265.68) --
	( 87.87,266.80) --
	( 90.89,267.93) --
	( 93.92,269.08) --
	( 96.95,270.25) --
	( 99.98,271.42) --
	(103.00,272.61) --
	(106.03,273.81) --
	(109.06,275.03) --
	(112.09,276.26) --
	(115.11,277.51) --
	(118.14,278.77) --
	(121.17,280.06) --
	(124.20,281.37) --
	(127.22,282.71) --
	(130.25,284.06) --
	(133.28,285.44) --
	(136.31,286.83) --
	(139.34,288.23) --
	(142.36,289.64) --
	(145.39,291.08) --
	(148.42,292.53) --
	(151.45,294.01) --
	(154.47,295.51) --
	(157.50,297.03) --
	(160.53,298.59) --
	(163.56,300.17) --
	(166.58,301.77) --
	(169.61,303.39) --
	(172.64,305.02) --
	(175.67,306.68) --
	(178.69,308.35) --
	(181.72,310.04) --
	(184.75,311.76) --
	(187.78,313.51) --
	(190.80,315.28) --
	(193.83,317.09) --
	(196.86,318.92) --
	(199.89,320.80) --
	(202.92,322.69) --
	(205.94,324.62) --
	(208.97,326.56) --
	(212.00,328.54) --
	(215.03,330.54) --
	(218.05,332.56) --
	(221.08,334.62) --
	(224.11,336.70) --
	(227.14,338.80) --
	(230.16,340.94) --
	(233.19,343.10) --
	(236.22,345.29) --
	(239.25,347.50) --
	(242.27,349.75) --
	(245.30,352.02) --
	(248.33,354.31) --
	(251.36,356.63) --
	(254.39,358.98) --
	(257.41,361.36) --
	(260.44,363.76) --
	(263.47,366.19) --
	(266.50,368.65);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 35.86,249.91) --
	( 38.88,250.76) --
	( 41.91,251.62) --
	( 44.94,252.51) --
	( 47.97,253.41) --
	( 50.99,254.32) --
	( 54.02,255.26) --
	( 57.05,256.21) --
	( 60.08,257.17) --
	( 63.10,258.15) --
	( 66.13,259.15) --
	( 69.16,260.17) --
	( 72.19,261.20) --
	( 75.21,262.25) --
	( 78.24,263.31) --
	( 81.27,264.39) --
	( 84.30,265.48) --
	( 87.33,266.60) --
	( 90.35,267.72) --
	( 93.38,268.87) --
	( 96.41,270.03) --
	( 99.44,271.21) --
	(102.46,272.41) --
	(105.49,273.62) --
	(108.52,274.84) --
	(111.55,276.08) --
	(114.57,277.32) --
	(117.60,278.59) --
	(120.63,279.86) --
	(123.66,281.16) --
	(126.68,282.48) --
	(129.71,283.81) --
	(132.74,285.17) --
	(135.77,286.56) --
	(138.79,287.97) --
	(141.82,289.39) --
	(144.85,290.83) --
	(147.88,292.29) --
	(150.91,293.76) --
	(153.93,295.24) --
	(156.96,296.75) --
	(159.99,298.28) --
	(163.02,299.84) --
	(166.04,301.42) --
	(169.07,303.03) --
	(172.10,304.67) --
	(175.13,306.33) --
	(178.15,308.01) --
	(181.18,309.70) --
	(184.21,311.42) --
	(187.24,313.15) --
	(190.26,314.90) --
	(193.29,316.68) --
	(196.32,318.49) --
	(199.35,320.33) --
	(202.37,322.21) --
	(205.40,324.12) --
	(208.43,326.06) --
	(211.46,328.03) --
	(214.49,330.03) --
	(217.51,332.06) --
	(220.54,334.11) --
	(223.57,336.19) --
	(226.60,338.30) --
	(229.62,340.44) --
	(232.65,342.61) --
	(235.68,344.80) --
	(238.71,347.02) --
	(241.73,349.28) --
	(244.76,351.56) --
	(247.79,353.87) --
	(250.82,356.21) --
	(253.84,358.58) --
	(256.87,360.97) --
	(259.90,363.40) --
	(262.93,365.85) --
	(265.95,368.33) --
	(268.98,370.84) --
	(272.01,373.38) --
	(275.04,375.95);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.39) --
	( 47.43,253.28) --
	( 50.45,254.18) --
	( 53.48,255.11) --
	( 56.51,256.05) --
	( 59.54,257.00) --
	( 62.56,257.98) --
	( 65.59,258.97) --
	( 68.62,259.97) --
	( 71.65,261.00) --
	( 74.67,262.04) --
	( 77.70,263.10) --
	( 80.73,264.17) --
	( 83.76,265.26) --
	( 86.78,266.37) --
	( 89.81,267.49) --
	( 92.84,268.63) --
	( 95.87,269.79) --
	( 98.89,270.97) --
	(101.92,272.16) --
	(104.95,273.37) --
	(107.98,274.60) --
	(111.01,275.84) --
	(114.03,277.11) --
	(117.06,278.38) --
	(120.09,279.67) --
	(123.12,280.97) --
	(126.14,282.28) --
	(129.17,283.61) --
	(132.20,284.96) --
	(135.23,286.33) --
	(138.25,287.72) --
	(141.28,289.14) --
	(144.31,290.58) --
	(147.34,292.05) --
	(150.36,293.53) --
	(153.39,295.03) --
	(156.42,296.54) --
	(159.45,298.06) --
	(162.48,299.61) --
	(165.50,301.18) --
	(168.53,302.77) --
	(171.56,304.38) --
	(174.59,306.03) --
	(177.61,307.70) --
	(180.64,309.41) --
	(183.67,311.14) --
	(186.70,312.89) --
	(189.72,314.66) --
	(192.75,316.45) --
	(195.78,318.25) --
	(198.81,320.09) --
	(201.83,321.94) --
	(204.86,323.83) --
	(207.89,325.76) --
	(210.92,327.71) --
	(213.94,329.71) --
	(216.97,331.74) --
	(220.00,333.80) --
	(223.03,335.89) --
	(226.06,338.01) --
	(229.08,340.16) --
	(232.11,342.33) --
	(235.14,344.54) --
	(238.17,346.77) --
	(241.19,349.04) --
	(244.22,351.34) --
	(247.25,353.67) --
	(250.28,356.02) --
	(253.30,358.41) --
	(256.33,360.83) --
	(259.36,363.28) --
	(262.39,365.76) --
	(265.41,368.27) --
	(268.44,370.81) --
	(271.47,373.38) --
	(274.50,375.98) --
	(277.52,378.61) --
	(280.55,381.26) --
	(283.58,383.95);
\definecolor{fillColor}{RGB}{230,159,0}

\path[fill=fillColor] ( 27.31,251.38) --
	( 30.68,245.55) --
	( 23.95,245.55) --
	cycle;

@@

\path[fill=fillColor] ( 95.65,273.63) --
	( 99.01,267.80) --
	( 92.29,267.80) --
	cycle;

\path[fill=fillColor] (129.82,287.78) --
	(133.18,281.95) --
	(126.46,281.95) --
	cycle;

\path[fill=fillColor] (163.99,304.26) --
	(167.35,298.43) --
	(160.63,298.43) --
	cycle;

\path[fill=fillColor] (198.16,323.63) --
	(201.52,317.81) --
	(194.79,317.81) --
	cycle;

\path[fill=fillColor] (232.33,346.20) --
	(235.69,340.37) --
	(228.96,340.37) --
	cycle;

\path[fill=fillColor] (266.50,372.59) --
	(269.86,366.77) --
	(263.13,366.77) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 33.36,247.39) --
	( 38.35,247.39) --
	( 38.35,252.38) --
	( 33.36,252.38) --
	cycle;

\path[fill=fillColor] ( 67.53,258.02) --
	( 72.52,258.02) --
	( 72.52,263.01) --
	( 67.53,263.01) --
	cycle;

\path[fill=fillColor] (101.70,270.61) --
	(106.69,270.61) --
	(106.69,275.61) --
	(101.70,275.61) --
	cycle;

\path[fill=fillColor] (135.86,285.30) --
	(140.86,285.30) --
	(140.86,290.30) --
	(135.86,290.30) --
	cycle;

\path[fill=fillColor] (170.03,302.36) --
	(175.03,302.36) --
	(175.03,307.36) --
	(170.03,307.36) --
	cycle;

\path[fill=fillColor] (204.20,322.52) --
	(209.20,322.52) --
	(209.20,327.51) --
	(204.20,327.51) --
	cycle;

\path[fill=fillColor] (238.37,345.90) --
	(243.37,345.90) --
	(243.37,350.89) --
	(238.37,350.89) --
	cycle;

\path[fill=fillColor] (272.54,373.53) --
	(277.54,373.53) --
	(277.54,378.53) --
	(272.54,378.53) --
	cycle;

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.83) -- ( 44.40,255.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.03,263.46) -- ( 82.10,263.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.57,259.93) -- ( 78.57,266.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.88,355.17) -- (252.94,355.17);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (249.41,351.64) -- (249.41,358.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.05,384.02) -- (287.11,384.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.58,380.49) -- (283.58,387.55);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 52.94,254.96) circle (  2.50);

\path[fill=fillColor] ( 87.11,266.50) circle (  2.50);

\path[fill=fillColor] (121.28,280.09) circle (  2.50);

@@

\path[fill=fillColor] (189.62,314.74) circle (  2.50);

\path[fill=fillColor] (223.78,336.55) circle (  2.50);

\path[fill=fillColor] (257.95,361.93) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Reproduction number $\mathcal R$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.06,332.94) rectangle (192.70,407.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 36.56,381.80) rectangle ( 51.02,396.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 38.01,389.03) -- ( 49.57,389.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-08-27 23:38:11
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.50) --
	( 30.02,248.23) --
	( 32.72,248.97) --
	( 35.42,249.73) --
	( 38.13,250.50) --
	( 40.83,251.28) --
	( 43.53,252.08) --
	( 46.24,252.88) --
	( 48.94,253.70) --
	( 51.64,254.53) --
	( 54.35,255.37) --
	( 57.05,256.23) --
	( 59.75,257.09) --
	( 62.46,257.97) --
	( 65.16,258.86) --
	( 67.86,259.76) --
	( 70.57,260.67) --
	( 73.27,261.60) --
	( 75.97,262.53) --
	( 78.67,263.48) --
	( 81.38,264.43) --
	( 84.08,265.40) --
	( 86.78,266.38) --
	( 89.49,267.37) --
	( 92.19,268.38) --
	( 94.89,269.40) --
	( 97.60,270.43) --
	(100.30,271.47) --
	(103.00,272.54) --
	(105.71,273.61) --
	(108.41,274.70) --
	(111.11,275.81) --
	(113.82,276.93) --
	(116.52,278.07) --
	(119.22,279.22) --
	(121.93,280.38) --
	(124.63,281.55) --
	(127.33,282.74) --
	(130.04,283.95) --
	(132.74,285.16) --
	(135.44,286.40) --
	(138.15,287.65) --
	(140.85,288.91) --
	(143.55,290.20) --
	(146.26,291.50) --
	(148.96,292.81) --
	(151.66,294.15) --
	(154.37,295.51) --
	(157.07,296.88) --
	(159.77,298.27) --
	(162.48,299.67) --
	(165.18,301.09) --
	(167.88,302.53) --
	(170.58,303.98) --
	(173.29,305.45) --
	(175.99,306.94) --
	(178.69,308.45) --
	(181.40,309.97) --
	(184.10,311.51) --
	(186.80,313.08) --
	(189.51,314.67) --
	(192.21,316.27) --
	(194.91,317.90) --
	(197.62,319.55) --
	(200.32,321.23) --
	(203.02,322.92) --
	(205.73,324.64) --
	(208.43,326.37) --
	(211.13,328.13) --
	(213.84,329.90) --
	(216.54,331.70) --
	(219.24,333.51) --
	(221.95,335.35) --
	(224.65,337.21) --
	(227.35,339.08) --
	(230.06,340.98) --
	(232.76,342.90) --
	(235.46,344.83) --
	(238.17,346.79) --
	(240.87,348.77);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 61.48,257.69) --
	( 64.19,258.56) --
	( 66.89,259.45) --
	( 69.59,260.35) --
	( 72.30,261.26) --
	( 75.00,262.19) --
	( 77.70,263.13) --
	( 80.40,264.08) --
	( 83.11,265.05) --
	( 85.81,266.03) --
	( 88.51,267.03) --
	( 91.22,268.04) --
	( 93.92,269.06) --
	( 96.62,270.09) --
	( 99.33,271.14) --
	(102.03,272.21) --
	(104.73,273.28) --
	(107.44,274.37) --
	(110.14,275.47) --
	(112.84,276.58) --
	(115.55,277.71) --
	(118.25,278.84) --
	(120.95,279.99) --
	(123.66,281.16) --
	(126.36,282.34) --
	(129.06,283.53) --
	(131.77,284.74) --
	(134.47,285.97) --
	(137.17,287.21) --
	(139.88,288.47) --
	(142.58,289.75) --
	(145.28,291.04) --
	(147.99,292.36) --
	(150.69,293.69) --
	(153.39,295.03) --
	(156.10,296.39) --
	(158.80,297.76) --
	(161.50,299.15) --
	(164.21,300.55) --
	(166.91,301.97) --
	(169.61,303.41) --
	(172.31,304.87) --
	(175.02,306.34) --
	(177.72,307.84) --
	(180.42,309.35) --
	(183.13,310.89) --
	(185.83,312.45) --
	(188.53,314.03) --
	(191.24,315.62) --
	(193.94,317.24) --
	(196.64,318.87) --
	(199.35,320.53) --
	(202.05,322.19) --
	(204.75,323.88) --
	(207.46,325.59) --
	(210.16,327.32) --
	(212.86,329.07) --
	(215.57,330.84) --
	(218.27,332.63) --
	(220.97,334.45) --
	(223.68,336.29) --
	(226.38,338.15) --
	(229.08,340.04) --
	(231.79,341.96) --
	(234.49,343.90) --
	(237.19,345.87) --
	(239.90,347.86) --
	(242.60,349.87) --
	(245.30,351.90) --
	(248.01,353.96) --
	(250.71,356.04) --
	(253.41,358.15) --
	(256.12,360.28) --
	(258.82,362.43) --
	(261.52,364.60) --
	(264.22,366.80) --
	(266.93,369.02) --
	(269.63,371.27) --
	(272.33,373.53) --
	(275.04,375.82);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 52.94,254.98) --
	( 55.64,255.81) --
	( 58.35,256.66) --
	( 61.05,257.53) --
	( 63.75,258.41) --
	( 66.46,259.30) --
	( 69.16,260.20) --
	( 71.86,261.12) --
	( 74.57,262.04) --
	( 77.27,262.99) --
	( 79.97,263.94) --
	( 82.68,264.91) --
	( 85.38,265.89) --
	( 88.08,266.89) --
	( 90.79,267.90) --
	( 93.49,268.92) --
	( 96.19,269.95) --
	( 98.89,271.00) --
	(101.60,272.05) --
	(104.30,273.12) --
	(107.00,274.20) --
	(109.71,275.30) --
	(112.41,276.40) --
	(115.11,277.52) --
	(117.82,278.66) --
	(120.52,279.81) --
	(123.22,280.97) --
	(125.93,282.15) --
	(128.63,283.34) --
	(131.33,284.55) --
	(134.04,285.78) --
	(136.74,287.03) --
	(139.44,288.29) --
	(142.15,289.56) --
	(144.85,290.85) --
	(147.55,292.16) --
	(150.26,293.48) --
	(152.96,294.81) --
	(155.66,296.16) --
	(158.37,297.52) --
	(161.07,298.90) --
	(163.77,300.30) --
	(166.48,301.72) --
	(169.18,303.16) --
	(171.88,304.61) --
	(174.59,306.09) --
	(177.29,307.58) --
	(179.99,309.10) --
	(182.70,310.64) --
	(185.40,312.20) --
	(188.10,313.77) --
	(190.80,315.36) --
	(193.51,316.96) --
	(196.21,318.59) --
	(198.91,320.23) --
	(201.62,321.89) --
	(204.32,323.58) --
	(207.02,325.28) --
	(209.73,327.01) --
	(212.43,328.76) --
	(215.13,330.54) --
	(217.84,332.33) --
	(220.54,334.16) --
	(223.24,336.01) --
	(225.95,337.88) --
	(228.65,339.78) --
	(231.35,341.70) --
	(234.06,343.64) --
	(236.76,345.60) --
	(239.46,347.59) --
	(242.17,349.60) --
	(244.87,351.63) --
	(247.57,353.69) --
	(250.28,355.76) --
	(252.98,357.86) --
	(255.68,359.99) --
	(258.39,362.13) --
	(261.09,364.30) --
	(263.79,366.49) --
	(266.50,368.71);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 44.40,252.37) --
	( 47.10,253.17) --
	( 49.80,253.99) --
	( 52.51,254.82) --
	( 55.21,255.66) --
	( 57.91,256.51) --
	( 60.62,257.37) --
	( 63.32,258.25) --
	( 66.02,259.14) --
	( 68.73,260.05) --
	( 71.43,260.97) --
	( 74.13,261.90) --
	( 76.84,262.84) --
	( 79.54,263.79) --
	( 82.24,264.76) --
	( 84.95,265.74) --
	( 87.65,266.74) --
	( 90.35,267.74) --
	( 93.06,268.76) --
	( 95.76,269.79) --
	( 98.46,270.83) --
	(101.17,271.88) --
	(103.87,272.95) --
	(106.57,274.03) --
	(109.28,275.12) --
	(111.98,276.23) --
	(114.68,277.35) --
	(117.39,278.49) --
	(120.09,279.64) --
	(122.79,280.80) --
	(125.49,281.98) --
	(128.20,283.18) --
	(130.90,284.39) --
	(133.60,285.61) --
	(136.31,286.85) --
	(139.01,288.09) --
	(141.71,289.35) --
	(144.42,290.63) --
	(147.12,291.92) --
	(149.82,293.22) --
	(152.53,294.54) --
	(155.23,295.88) --
	(157.93,297.23) --
	(160.64,298.61) --
	(163.34,300.00) --
	(166.04,301.41) --
	(168.75,302.85) --
	(171.45,304.30) --
	(174.15,305.78) --
	(176.86,307.28) --
	(179.56,308.79) --
	(182.26,310.32) --
	(184.97,311.86) --
	(187.67,313.42) --
	(190.37,315.01) --
	(193.08,316.61) --
	(195.78,318.23) --
	(198.48,319.88) --
	(201.19,321.54) --
	(203.89,323.23) --
	(206.59,324.94) --
	(209.30,326.68) --
	(212.00,328.43) --
	(214.70,330.22) --
	(217.40,332.02) --
	(220.11,333.85) --
	(222.81,335.71) --
	(225.51,337.58) --
	(228.22,339.48) --
	(230.92,341.40) --
	(233.62,343.34) --
	(236.33,345.30) --
	(239.03,347.28) --
	(241.73,349.29) --
	(244.44,351.32) --
	(247.14,353.37) --
	(249.84,355.45) --
	(252.55,357.54) --
	(255.25,359.66) --
	(257.95,361.80);
\definecolor{drawColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 1pt off 3pt ,line join=round] ( 35.86,249.88) --
	( 38.56,250.65) --
	( 41.26,251.43) --
	( 43.97,252.22) --
	( 46.67,253.03) --
	( 49.37,253.84) --
	( 52.07,254.67) --
	( 54.78,255.51) --
	( 57.48,256.37) --
	( 60.18,257.24) --
	( 62.89,258.11) --
	( 65.59,259.01) --
	( 68.29,259.91) --
	( 71.00,260.83) --
	( 73.70,261.76) --
	( 76.40,262.70) --
	( 79.11,263.65) --
	( 81.81,264.62) --
	( 84.51,265.60) --
	( 87.22,266.59) --
	( 89.92,267.59) --
	( 92.62,268.60) --
	( 95.33,269.63) --
	( 98.03,270.67) --
	(100.73,271.72) --
	(103.44,272.79) --
	(106.14,273.87) --
	(108.84,274.96) --
	(111.55,276.07) --
	(114.25,277.19) --
	(116.95,278.32) --
	(119.66,279.47) --
	(122.36,280.64) --
	(125.06,281.81) --
	(127.77,283.00) --
	(130.47,284.20) --
	(133.17,285.41) --
	(135.88,286.63) --
	(138.58,287.87) --
	(141.28,289.12) --
	(143.98,290.39) --
	(146.69,291.67) --
	(149.39,292.97) --
	(152.09,294.29) --
	(154.80,295.63) --
	(157.50,296.98) --
	(160.20,298.36) --
	(162.91,299.76) --
	(165.61,301.18) --
	(168.31,302.62) --
	(171.02,304.07) --
	(173.72,305.54) --
	(176.42,307.02) --
	(179.13,308.53) --
	(181.83,310.05) --
	(184.53,311.59) --
	(187.24,313.15) --
	(189.94,314.73) --
	(192.64,316.33) --
	(195.35,317.95) --
	(198.05,319.60) --
	(200.75,321.27) --
	(203.46,322.96) --
	(206.16,324.67) --
	(208.86,326.41) --
	(211.57,328.16) --
	(214.27,329.94) --
	(216.97,331.74) --
	(219.68,333.57) --
	(222.38,335.41) --
	(225.08,337.27) --
	(227.79,339.16) --
	(230.49,341.07) --
	(233.19,342.99) --
	(235.89,344.94) --
	(238.60,346.91) --
	(241.30,348.91) --
	(244.00,350.92) --
	(246.71,352.95) --
	(249.41,355.01);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] (104.19,276.95) --
	(107.56,271.12) --
	(100.83,271.12) --
	cycle;

\path[fill=fillColor] (146.90,295.71) --
	(150.27,289.89) --
	(143.54,289.89) --
	cycle;

\path[fill=fillColor] (189.62,318.55) --
	(192.98,312.72) --
	(186.25,312.72) --
	cycle;

\path[fill=fillColor] (232.33,346.23) --
	(235.69,340.41) --
	(228.96,340.41) --
	cycle;

\path[fill=fillColor] (275.04,379.71) --
	(278.40,373.88) --
	(271.67,373.88) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

\path[fill=fillColor] ( 50.44,252.48) --
	( 55.44,252.48) --
	( 55.44,257.47) --
	( 50.44,257.47) --
	cycle;

\path[fill=fillColor] ( 93.15,267.25) --
	( 98.15,267.25) --
	( 98.15,272.24) --
	( 93.15,272.24) --
	cycle;

\path[fill=fillColor] (135.86,285.28) --
	(140.86,285.28) --
	(140.86,290.28) --
	(135.86,290.28) --
	cycle;

\path[fill=fillColor] (178.58,307.22) --
	(183.57,307.22) --
	(183.57,312.21) --
	(178.58,312.21) --
	cycle;

\path[fill=fillColor] (221.29,333.88) --
	(226.28,333.88) --
	(226.28,338.88) --
	(221.29,338.88) --
	cycle;

\path[fill=fillColor] (264.00,366.21) --
	(268.99,366.21) --
	(268.99,371.20) --
	(264.00,371.20) --
	cycle;
\definecolor{drawColor}{RGB}{0,158,115}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 44.40,248.84) -- ( 44.40,255.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.54) -- ( 90.64,266.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.01) -- ( 87.11,270.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.90) -- (133.35,283.90);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.37) -- (129.82,287.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.89) -- (176.06,304.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.36) -- (172.53,308.43);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.58) -- (218.77,330.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (215.24,327.04) -- (215.24,334.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (254.42,361.80) -- (261.49,361.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.95,358.27) -- (257.95,365.33);
\definecolor{drawColor}{RGB}{240,228,66}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,247.39) rectangle ( 38.35,252.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,247.39) -- ( 38.35,252.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 33.36,252.38) -- ( 38.35,247.39);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,260.97) rectangle ( 81.06,265.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,260.97) -- ( 81.06,265.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 76.07,265.96) -- ( 81.06,260.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,277.67) rectangle (123.78,282.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,277.67) -- (123.78,282.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.78,282.67) -- (123.78,277.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,297.83) rectangle (166.49,302.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,297.83) -- (166.49,302.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (161.49,302.82) -- (166.49,297.83);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,322.52) rectangle (209.20,327.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,322.52) -- (209.20,327.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (204.20,327.51) -- (209.20,322.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,352.51) rectangle (251.91,357.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,352.51) -- (251.91,357.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (246.91,357.51) -- (251.91,352.51);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 27.31,247.50) circle (  2.50);

\path[fill=fillColor] ( 70.02,260.49) circle (  2.50);

\path[fill=fillColor] (112.74,276.48) circle (  2.50);

@@

\path[fill=fillColor] (198.16,319.89) circle (  2.50);

\path[fill=fillColor] (240.87,348.77) circle (  2.50);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 13.08,329.23) {Basic reproduction number $\mathcal R_0$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 37.78,389.03) rectangle ( 52.24,403.48);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 39.23,396.25) -- ( 50.79,396.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor] ( 45.01,396.25) circle (  2.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,433.62);
\definecolor{fillColor}{RGB}{255,255,255}
